---
title: "Report"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
params: 
  lacytools_summary: NA
  plate_design: NA
  metadata: NA
  manual_sample_types: NA
  sample_types_file: NA
  mass_acc: NA
  ipq: NA
  sn: NA
  spectra_curation_cut_off: NA
  spectra_curation_plot: NA
  analyte_curation_method: NA
  ignore_samples: NA
  cut_off_percentage: NA
  analyte_list: NA
  analyte_curation_plot: NA
  analyte_curation_table: NA
  derived_traits: NA
  repeatability_1: NA
  repeatability_2: NA
  data_exploration_plot: NA
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Data import

- LacyTools summary file: `r paste0("\"", params$lacytools_summary, "\"")`
- Plate design file(s): `r paste0("\"", params$plate_design, "\"")`
- Metadata file(s): `r ifelse(is.null(params$metadata), "none", paste0("\"", paste(params$metadata, collapse = " and "), "\""))`

Sample types were added `r ifelse(params$manual_sample_types, "manually", "automatically")`.

```{r results='asis'}

if (params$manual_sample_types) {
  text <- cat("Sample types file: \"",
            params$sample_types_file,
            "\"")
}

```

## Spectra curation

- Analyte quality criteria:
  - Acceptable mass accuracy range: `r min(params$mass_acc)` - `r max(params$mass_acc)`
  - Max. IPQ value: `r params$ipq`
  - Min. S/N ratio: `r params$sn`
- Basis for spectra curation cut-off: `r params$spectra_curation_cut_off`  


```{r spectra-curation-plot, results='markup'}

params$spectra_curation_plot +
  ggplot2::theme(text = ggplot2::element_text(size = 12))

```


## Analyte curation


```{r analyte-curation, results='asis'}

if (params$analyte_curation_method == "Curate analytes based on data") {
  text <- paste0(params$ignore_samples, collapse = ", ")
  cat(
      "- Method: based on data\n",
      "- Samples excluded from analyte curation:",
      text,
      "\n- Cut-off percentage:",
      params$cut_off,
      "%")
}

if (params$analyte_curation_method == "Supply an analyte list") {
  cat(
    "- Method: based on analyte list\n",
    "- Analyte list file: \"",
    params$analyte_list,
    "\""
  )
}

```

```{r analyte-curation-plot-table, results='asis'}

if (params$analyte_curation_method == "Curate analytes based on data") {
  
  tables <- params$analyte_curation_plot[stringr::str_subset(
    string = names(params$analyte_curation_plot),
    pattern = "table")]
  plots <- params$analyte_curation_plot[stringr::str_subset(
    string = names(params$analyte_curation_plot),
    pattern = "plot")]
  
  print(names(tables))
  print(names(plots))
  
  for (table in tables) {
    table %>% 
      kableExtra::kbl() %>% 
      kableExtra::kable_styling(bootstrap_options = "striped", 
                                full_width = F, 
                                position = "left") %>% 
      htmltools::HTML() %>% 
      print()
  }
  
  for (plot in plots) {
    print(plot)
  }
  
}

```

## Derived traits

```{r derived-traits, results='asis'}

if (is.null(params$derived_traits)) {
  cat("No derived traits were calculated")
} else {
  cat("The following derived traits were calculated:\n\n- ",
      paste(params$derived_traits, collapse = "\n- "))
}

```

## Repeatability

```{r repeatability-plots, results='asis', warning=FALSE}

print(params$repeatability_1$plot)

params$repeatability_1$for_table %>% 
      kableExtra::kbl() %>% 
      kableExtra::kable_styling(bootstrap_options = "striped", 
                                full_width = F, 
                                position = "left") %>% 
      htmltools::HTML() %>% 
      print()


if (!is.null(params$repeatability_2$plot)) {
  print(params$repeatability_1$plot)
}

if (!is.null(params$repeatability_2$for_table)) {
  params$repeatability_2$for_table %>% 
      kableExtra::kbl() %>% 
      kableExtra::kable_styling(bootstrap_options = "striped", 
                                full_width = F, 
                                position = "left") %>% 
      htmltools::HTML() %>% 
      print()
}

```

## Data exploration

```{r data-exploration-plot, results='markup'}

params$data_exploration_plot

```

