---
title: "glycodash"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{glycodash}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}

#library(glycodash)
devtools::load_all()

```

This vignette is not yet finished!

## Data import

The data import functions can be used to convert a LacyTools summary file to a format suitable for R.

```{r reading-the-lacytools-summary}

lacytools_file <- system.file("extdata",
                              "LacyTools_summary_example.txt", 
                              package = "glycodash")

raw_data <- read_non_rectangular(lacytools_file)

data <- read_lacytools_summary(raw_data) %>% 
  detect_group(.,
               keyword_specific = "Spike",
               keyword_total = "Total")

data

```

In addition, a plate design file can be processed to add sample types and sample ID's to the data.

```{r processing-the-plate-design}

plate_design_file <- system.file("extdata",
                                 "Plate_design_example.xlsx",
                                 package = "glycodash")



plate_design <- read_and_process_plate_design(plate_design_file)

data_with_platewell <- detect_plate_and_well(data)

data_complete <- dplyr::left_join(data_with_platewell,
                                  plate_design) %>% 
  tidyr::extract(col = sample_id,
                 into = c("sample_type"),
                 regex = "([[:alpha:]]+)",
                 remove = FALSE) %>% 
  define_clusters(.,
                  cluster_keywords = "IgGI1")

replicates <- data_complete %>% 
        dplyr::select(tidyselect::any_of(c("sample_name", "sample_id", "group"))) %>% 
        dplyr::distinct() %>% 
        dplyr::group_by(dplyr::across(tidyselect::any_of("group"))) %>% 
        dplyr::add_count(sample_id, name = "number_of_replicates") %>% 
        dplyr::mutate(number_of_replicates = ifelse(sample_id == "empty cell in plate design",
                                                    1,
                                                    number_of_replicates)) %>% 
        dplyr::mutate(replicates = ifelse(number_of_replicates > 1, 
                                          TRUE, 
                                          FALSE))
      
data_complete <- dplyr::full_join(replicates, data_complete) %>% 
  dplyr::ungroup(.)

data_complete

```

Finally, metadata can be added to the data.

```{r adding-metadata, eval=FALSE}

metadata_file <- system.file("extdata",
                            "Metadata_example.xlsx",
                            package = "glycodash")

metadata <- read_metadata(metadata_file,
                          "Metadata_example.xlsx")

metadata

data <- dplyr::left_join(data,
                         metadata,
                         by = c(sample_id = "sample_id"))

x <- data %>% 
  dplyr::group_by(sample_name) %>% 
  dplyr::filter(!all(is.na(absolute_intensity_background_subtracted))) %>% 
  dplyr::filter(sample_id == "PBS")

unique(x$sample_name)

```

## Spectra curation

The spectra curation functions can be used to curate spectra, based on the 
proportion of analytes within the spectrum that fulfill the analyte quality 
criteria and based on the sum intensity of those passing analytes within the 
spectrum. This proportion of passing analytes and this sum intensity are compared
to the cut-off values for both. The cut-off values are the average 
proportion of passing analytes and average sum intensity + 3 times the standard 
deviations in a chosen group of spectra that should not pass curation (cut_off_basis). 

```{r spectra-curation}

checked_data <- do_criteria_check(data_complete,
                       min_ppm_deviation = -20,
                       max_ppm_deviation = 20,
                       max_ipq = 0.2,
                       min_sn = 9)

summarized_checks <- check_spectra(data = data_complete,
                                 min_ppm_deviation = -20,
                                 max_ppm_deviation = 20,
                                 max_ipq = 0.2,
                                 min_sn = 9)

cut_offs <- calculate_cut_offs(summarized_checks,
                               c("Spike PBS", "Total PBS"),
                               3,
                               "Mean")


data_curated <- curate_spectra(checked_data,
                       summarized_checks,
                       cut_offs) %>% 
  dplyr::filter(passed_spectra_curation == TRUE)

```

## Analyte curation

```{r analyte-curation}

curated_analytes <- curate_analytes(data = data_curated,
                                    cut_off_percentage = 25)

analyte_curated_data <- dplyr::left_join(curated_analytes, 
                                         data_curated)

plot_analyte_curation(curated_analytes = curated_analytes,
                      cut_off_percentage = 25,
                      selected_cluster = "IgGI1") 

dataframe_for_table <- prepare_analyte_curation_table(
  analyte_curated_data = analyte_curated_data,
  selected_cluster = "IgGI1")

dataframe_for_table

charge_columns <- colnames(dataframe_for_table)[-1]

analytes_to_include <- rlang::set_names(charge_columns) %>% 
  purrr::map_dfc(.,
                 function(charge_column) {
                   print(charge_column)
                   ifelse(dataframe_for_table[[charge_column]] == "Yes",
                          dataframe_for_table$analyte,
                          NA)
                 }) %>% 
  tidyr::pivot_longer(
    tidyselect::everything(),
    names_to = "charge",
    values_to = "analyte"
  ) %>% 
  dplyr::filter(!is.na(analyte)) %>% 
  dplyr::mutate(dplyr::across(analyte, as.character))

data_for_norm <- dplyr::left_join(analytes_to_include,
                 data_curated)

```

```{r normalization}

total_intensities <- calculate_total_intensity(data = data_for_norm)
normalized_data <- normalize_data(data = total_intensities) 
normalized_data_wide <- normalized_data %>% 
        # removing columns with values that differ between clusters:
        dplyr::select(-tidyselect::any_of(c("passing_proportion", 
                                            "cut_off_prop", 
                                            "cut_off_sum_int"))) %>% 
        tidyr::pivot_wider(names_from = c(cluster, analyte),
                           names_sep = "_",
                           values_from = relative_abundance)

#normalized_data_wide <- normalized_data_wide %>% dplyr::select(-group)

menu <- normalized_data %>% 
  dplyr::select(tidyselect::any_of(c("sample_name", "group", "sample_id"))) %>%
  dplyr::distinct() %>%
  dplyr::group_by(dplyr::across(tidyselect::any_of("group"))) %>% 
  dplyr::add_count(sample_id, name = "number_of_replicates_after_curation") %>% 
  dplyr::mutate(number_of_replicates_after_curation = ifelse(sample_id == "empty cell in plate design",
                                              1,
                                              number_of_replicates_after_curation)) %>% 
  dplyr::mutate(replicates_after_curation = number_of_replicates_after_curation > 1) %>% 
  dplyr::distinct(dplyr::across(tidyselect::any_of(c("group", "sample_id")))) %>% 
  purrr::pmap_chr(.,
                  paste)

selected_sample_id <- stringr::str_extract(menu[2],
                                             unique(normalized_data$sample_id)) %>% 
  na.omit()

if ("group" %in% colnames(normalized_data)) {
  selected_group <- stringr::str_extract(
    string = menu[2],
    pattern = unique(normalized_data$group)) %>% 
    na.omit(.)
} else {
  selected_group <- NULL
}

repeatability <- calculate_repeatability_stats(normalized_data,
                                               selected_sample_id,
                                               selected_group)

to_plot <- normalized_data %>% 
  dplyr::filter(sample_id == selected_sample_id,
                group == selected_group) %>% 
  dplyr::group_by(analyte) %>% 
  dplyr::summarize(mean_rel_ab = mean(relative_abundance),
                   sd_rel_ab = sd(relative_abundance),
                   rsd = sd_rel_ab / mean_rel_ab,
                   n = dplyr::n(),
                   dplyr::across())


means <- to_plot %>% 
  dplyr::group_by(analyte) %>% 
  dplyr::summarize(mean_rel_ab = mean(relative_abundance),
                   sd_rel_ab = sd(relative_abundance),
                   rsd = sd_rel_ab / mean_rel_ab,
                   n = dplyr::n(),
                   dplyr::across())

n_colors <- length(unique(to_plot$sample_name))
my_palette <- colorRampPalette(RColorBrewer::brewer.pal(8, "Set2"))(n_colors)

dodged_barplot <- ggplot2::ggplot(to_plot) +
  ggplot2::geom_col(ggplot2::aes(x = analyte, 
                                 y = relative_abundance,
                                 fill = sample_name,
                                 text = paste("Analyte:",
                                 analyte,
                                 "\nSample name:",
                                 sample_name,
                                 "\nRelative abundance:",
                                 signif(relative_abundance * 100, 3),
                                 "%"),),
                    position = "dodge") +
  ggplot2::geom_point(data = to_plot %>% dplyr::distinct(analyte, .keep_all = TRUE),
                         ggplot2::aes(x = analyte, 
                                 y = rsd,
                                 fill = sample_name,
                                 text = paste("RSD:",
                                              signif(rsd * 100, 3),
                                              "%")),
                      shape = 21,
                      stroke = 0.5)+
  ggplot2::theme_classic() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45,
                                                     hjust = 1),
                 panel.border = ggplot2::element_rect(colour = "black", fill=NA, size=0.5),
                 legend.position = "none") +
  ggplot2::scale_y_continuous(name = "Relative abundance (%)",
                              labels = function(x) paste0(x * 100, "%")) +
  ggplot2::scale_x_discrete(name = "Analyte") +
  ggplot2::scale_fill_manual(values = my_palette,
                                name = "Sample name") +
  ggplot2::facet_wrap(~ cluster, scales = "free_x")

n_colors <- length(unique(means$analyte))
my_palette2 <- colorRampPalette(RColorBrewer::brewer.pal(8, "Set2"))(n_colors)

mean_barplot <- ggplot2::ggplot(means) +
  ggplot2::geom_col(ggplot2::aes(x = analyte, 
                                 y = mean_rel_ab,
                                 text = paste("Analyte:",
                                 analyte,
                                 "\nMean of relative abundance:",
                                 signif(mean_rel_ab * 100, 3),
                                 "%",
                                 "\nNumber of samples (n):",
                                 n),
                                 fill = analyte),
                    position = "dodge",
                    color = "black") +
  ggplot2::geom_errorbar(ggplot2::aes(ymin = mean_rel_ab - sd_rel_ab,
                                      ymax = mean_rel_ab + sd_rel_ab,
                                      x = analyte,
                                      text = paste("Standard deviation:",
                                                   signif(sd_rel_ab * 100, 3),
                                                   "%"
                                        # "Mean - standard deviation:",
                                        #            signif((mean_rel_ab - sd_rel_ab) * 100, 3),
                                        #            "%",
                                        #            "\nMean + standard deviation:",
                                        #            signif((mean_rel_ab + sd_rel_ab) * 100, 3),
                                        #            "%"
                                        ))) +
  ggplot2::geom_point(ggplot2::aes(x = analyte, 
                                 y = rsd,
                                 fill = analyte,
                                 text = paste("RSD:",
                                              signif(rsd * 100, 3),
                                              "%")),
                      shape = 21,
                      stroke = 0.5
                      )+
  ggplot2::scale_fill_manual(values = my_palette2) +
  ggplot2::theme_classic() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45,
                                                     hjust = 1),
                 panel.border = ggplot2::element_rect(colour = "black", fill=NA, size=0.5),
                 legend.position = "none") +
  ggplot2::scale_y_continuous(name = "Relative abundance (%)",
                              labels = function(x) paste0(x * 100, "%")) +
  ggplot2::scale_x_discrete(name = "Analyte") +
  ggplot2::facet_wrap(~ cluster, scales = "free_x")

plotly::ggplotly(dodged_barplot, tooltip = "text")
plotly::ggplotly(mean_barplot, tooltip = "text")

        
plot <- visualize_repeatability2(repeatability)

pl <- plotly::ggplotly(plot, tooltip = "text")

pl


```

