---
title: "glycodash"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{glycodash}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}

#library(glycodash)
devtools::load_all()

```

This vignette is not yet finished!

## Data import

The data import functions can be used to convert a LacyTools summary file to a format suitable for R.

```{r reading-the-lacytools-summary}

lacytools_file <- system.file("extdata",
                              "LacyTools_summary_example.txt", 
                              package = "glycodash")

raw_data <- read_non_rectangular(lacytools_file)

data <- read_lacytools_summary(raw_data) %>% 
  detect_group(.,
               keyword_specific = "Spike",
               keyword_total = "Total")

data

```

In addition, a plate design file can be processed to add sample types and sample ID's to the data.

```{r processing-the-plate-design}

plate_design_file <- system.file("extdata",
                                 "Plate_design_example.xlsx",
                                 package = "glycodash")



plate_design <- read_and_process_plate_design(plate_design_file)

data_with_platewell <- detect_plate_and_well(data)

data_complete <- dplyr::left_join(data_with_platewell,
                                  plate_design) %>% 
  tidyr::extract(col = sample_id,
                 into = c("sample_type"),
                 regex = "([[:alpha:]]+)",
                 remove = FALSE) %>% 
  define_clusters(.,
                  cluster_keywords = "IgGI1")

data_complete

```

Finally, metadata can be added to the data.

```{r adding-metadata, eval=FALSE}

metadata_file <- system.file("extdata",
                            "Metadata_example.xlsx",
                            package = "glycodash")

metadata <- read_metadata(metadata_file,
                          "Metadata_example.xlsx")

metadata

data <- dplyr::left_join(data,
                         metadata,
                         by = c(sample_id = "sample_id"))

x <- data %>% 
  dplyr::group_by(sample_name) %>% 
  dplyr::filter(!all(is.na(absolute_intensity_background_subtracted))) %>% 
  dplyr::filter(sample_id == "PBS")

unique(x$sample_name)

```

## Spectra curation

The spectra curation functions can be used to curate spectra, based on the 
proportion of analytes within the spectrum that fulfill the analyte quality 
criteria and based on the sum intensity of those passing analytes within the 
spectrum. This proportion of passing analytes and this sum intensity are compared
to the cut-off values for both. The cut-off values are the average 
proportion of passing analytes and average sum intensity + 3 times the standard 
deviations in a chosen group of spectra that should not pass curation (cut_off_basis). 

```{r spectra-curation}

checked_data <- do_criteria_check(data_complete,
                       min_ppm_deviation = -20,
                       max_ppm_deviation = 20,
                       max_ipq = 0.2,
                       min_sn = 9)

checked_spectra <- check_spectra(data = data_complete,
                                 min_ppm_deviation = -20,
                                 max_ppm_deviation = 20,
                                 max_ipq = 0.2,
                                 min_sn = 9)

cut_offs <- calculate_cut_offs(checked_spectra,
                               c("Spike PBS", "Total PBS"))

passing_spectra <- checked_spectra %>% 
  dplyr::mutate(cut_off_sum_int = cut_offs$cut_off_sum_int,
                cut_off_prop = cut_offs$cut_off_prop) %>% 
  dplyr::filter((passing_proportion > cut_off_prop) & (sum_intensity > cut_off_sum_int)) %>% 
  dplyr::mutate(passed_spectra_curation = TRUE)

data_curated <- dplyr::full_join(passing_spectra, 
                                 checked_data) %>% 
    dplyr::mutate(passed_spectra_curation = tidyr::replace_na(passed_spectra_curation, 
                                                              FALSE))


data_curated

test <- curate_spectra(checked_data,
                       checked_spectra,
                       cut_offs)

```

## Analyte curation

```{r analyte-curation}

curated_analytes <- curate_analytes(data = spectra_curation$curated_data,
                                    group_to_ignore = "Total",
                                    sample_types_to_ignore = c("Visucon", 
                                                               "PBS"),
                                    cut_off_percentage = 25)

passing_analytes <- curated_analytes %>% 
  dplyr::filter(passed_curation == TRUE) %>% 
  dplyr::select(-passed_curation)

data <- dplyr::left_join(passing_analytes, 
                         data)

data

plot_analyte_curation(curated_analytes = curated_analytes,
                      cut_off_percentage = 25,
                      selected_cluster = "IgGI1") 

dataframe_for_table <- prepare_analyte_curation_table(
  analyte_curated_data = data,
  selected_cluster = "IgGI1")

dataframe_for_table

```


