---
title: "GlycoDash v1.6.0 data processing report"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
params: 
  data_type: NA
  summary_filenames: NA
  plate_design: NA
  sample_list: NA
  filenames_metadata: NA
  sample_types_method: NA
  filename_sample_types: NA
  mass_acc: NA
  ipq: NA
  sn: NA
  idp: NA
  total_area: NA
  included_qc_spectra: NA
  spectra_curation_tab_contents: NA
  curated_spectra_plot: NA
  curated_spectra_plots: NA
  analyte_curation_method: NA
  analyte_curation_choice: NA
  included_qc_analytes: NA
  ignore_samples: NA
  groups_to_ignore: NA
  cut_offs: NA
  analyte_list: NA
  analyte_curation_tab_contents: NA
  heatmaps: NA
  heatmaps_excluded_sample_types: NA
  derived_traits: NA
  custom_traits_colnames: NA
  formulas: NA
  custom_formulas: NA
  intensity_plots: NA
  repeatability: NA
  data_exploration: NA
  silumab_amount: NA
  chosen_peptides: NA
  quantitation_plot: NA
  peptide_correlation_plots: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(magrittr)
```

```{r, include=FALSE}
# Init Step to make sure that the dependencies are loaded
htmltools::tagList(DT::datatable(cars))
htmltools::tagList(plotly::ggplotly(ggplot2::ggplot()))
```

## Data import

-   Uploaded files: `r paste0("\"", params$summary_filenames, "\"")`
-   Plate design file(s): `r paste0("\"", params$plate_design, "\"")`
-   Sample list file: `r ifelse(is.null(params$metadata), "none", paste0("\"", params$sample_list, "\""))`
-   Metadata file(s): `r ifelse(is.null(params$filenames_metadata), "none", paste0("\"", params$filenames_metadata, "\""))`

Sample types were added `r ifelse(params$sample_types_method == "Automatically determine sample types based on sample ID's", "automatically", "manually")`.

```{r results='asis'}

if (params$sample_types_method != "Automatically determine sample types based on sample ID's") {
  cat(paste0("Sample types file: \"",
             params$filename_sample_types,
             "\""))
}

```

## Spectra curation

-   Analyte quality criteria:

    ```{r results='asis'}

    if (params$data_type == "LaCyTools data") {
      cat("- Acceptable mass accuracy range (ppm): ", min(params$mass_acc), 
          "-", max(params$mass_acc))
      cat("\n- Max. IPQ value: ", params$ipq)
      cat("\n- Min. S/N ratio: ", params$sn)
    } else if (params$data_type == "Skyline data") {
      cat("- Acceptable mass accuracy range (ppm): ", min(params$mass_acc), 
          "-", max(params$mass_acc))
      cat("\n- Min. IDP value: ", params$idp)
      cat("\n- Min. total area: ", params$total_area)
    }
    ```

The following analyte quality criteria were taken into account in the calculation of the cut-off for the percentage of passing analytes: `r params$included_qc_spectra`

### Spectra curation cut-offs

```{r spectra-curation-cut-offs, results='asis'}

purrr::iwalk(params$spectra_curation_tab_contents, 
             function(objects_list,
                      name) {
               
               cat("####",
                     name,
                     "\n")
               
               objects_list$table %>%
                 kableExtra::kbl() %>%
                 kableExtra::kable_styling(bootstrap_options = "striped",
                                           full_width = F,
                                           position = "left") %>%
                 htmltools::HTML() %>%
                 print()
               
               p <- objects_list$plot %>% 
                 plotly::ggplotly(., tooltip = "text")
               
               p[["x"]][["layout"]][["annotations"]][[2]][["xshift"]] <- -70
               
               p[["x"]][["layout"]][["margin"]][["l"]] <- 90
               
               p <- GlycoDash::facet_strip_bigger(p)
               
               print(htmltools::tagList(p))
             })

```

### Spectra curation results

```{r spectra-curation-results, results='asis'}

#TODO: add titles

if (!is.null(params$curated_spectra_plot)) {
  p <- params$curated_spectra_plot %>% 
    plotly::ggplotly(., tooltip = "text")
  
  p <- GlycoDash::facet_strip_bigger(p)
  
  p[["x"]][["layout"]][["annotations"]][[2]][["xshift"]] <- -50
  
  p[["x"]][["layout"]][["annotations"]][[1]][["yshift"]] <- -50
  
  print(htmltools::tagList(p))
} else {
  purrr::iwalk(params$curated_spectra_plots,
             function(curated_spectra_plot,
                      name) {
               
               cat("####",
                     name,
                     "\n")
               
               p <- curated_spectra_plot %>% 
                 plotly::ggplotly(., tooltip = "text")
               
               p <- GlycoDash::facet_strip_bigger(p)
               
               p[["x"]][["layout"]][["annotations"]][[2]][["xshift"]] <- -50
               
               p[["x"]][["layout"]][["annotations"]][[1]][["yshift"]] <- -50
               
               print(htmltools::tagList(p))
             })
}


```

## Analyte curation

The following analyte quality criteria were taken into account in the analyte curation: `r params$included_qc_analytes`

```{r analyte-curation, results='asis'}

if (params$analyte_curation_method == "Supply an analyte list") {
  cat(
    "- Curation method: based on analyte list\n",
    "- Analyte list file: \"",
    params$analyte_list,
    "\""
  )
}

if (params$analyte_curation_method == "Curate analytes based on data") {
  if (params$analyte_curation_choice == "On all data") {
    text <- paste0(params$ignore_samples, collapse = ", ")
      cat(
      "- Curation method: based on all data\n",
      paste("- Samples excluded from analyte curation:", text, "\n"),
      "- Cut-off percentages:",
      paste(names(params$cut_offs), ": ", params$cut_offs, "%, ", sep = "", collapse = "\n")
      )
  } else if (params$analyte_curation_choice == "Per biological group") {
    text <- paste0(params$groups_to_ignore, collapse = ", ")
    cat(
      "- Curation method: per biological group\n",
      paste("- Biological groups excluded from analyte curation:", text, "\n"),
      "- Cut-off percentages:",
      paste(names(params$cut_offs), ": ", params$cut_offs, "%, ", sep = "", collapse = "\n")
    )
  } else if (params$analyte_curation_choice == "Per sample") {
    cat("Curation method: per sample")
  }
}
```

```{r analyte-curation-plot-table, results='asis'}

if (params$analyte_curation_method == "Curate analytes based on data") {
  
  purrr::iwalk(params$analyte_curation_tab_contents, 
               function(objects_list,
                        name) {
                 cat("###",
                     name,
                     "\n")
                 
                 p <- objects_list$plot %>% 
                   plotly::ggplotly(., tooltip = "text")
                 
                 p[["x"]][["layout"]][["annotations"]][[2]][["xshift"]] <- -50
                 
                 p[["x"]][["layout"]][["annotations"]][[1]][["yshift"]] <- -90
                 
                 print(htmltools::tagList(p))
                 
                 objects_list$analytes_to_include %>% 
                   tidyr::pivot_wider(names_from = "charge",
                                      names_glue = "{charge} charge state included?",
                                      values_from = "charge",
                                      values_fn = function(value) { "Yes" },
                                      values_fill = "No") %>%
                   kableExtra::kbl() %>%
                   kableExtra::kable_styling(bootstrap_options = "striped",
                                             full_width = F,
                                             position = "left") %>%
                   kableExtra::scroll_box(height = "500px", width = "100%") %>% 
                   htmltools::HTML() %>%
                   print()
                 
               })
               
               }

```

## Normalized data heatmaps

```{r excluded_sample_types, results='asis'}

cat(paste(
  "Sample types excluded from heatmaps: ",
  paste(params$heatmaps_excluded_sample_types, collapse = ", ")
))
```

```{r heatmaps, results='asis'}

if (!is.null(names(params$heatmaps))) {
  # Heatmaps were made per cluster
  purrr::iwalk(params$heatmaps, function(plot, name) {
    cat("###", name, "\n")
    p <- plotly::ggplotly(plot, tooltip = "text")
    print(htmltools::tagList(p))
  })
} else {
  # One heatmap with clusters on y-axis
  p <- plotly::ggplotly(params$heatmaps[[1]], tooltip = "text")
  print(htmltools::tagList(p))
}

```

## IgG1 quantitation

```{r IgG1-quantitation-peptides, results='asis'}

if (is.null(params$quantitation_plot)) {
  cat("IgG1 was not quantified.")
} else {
  cat("IgG1 was quantified with SILuMAb based on the following peptides:",
      paste(params$chosen_peptides, collapse = ", "))
}
```

Peptide correlation plots:

```{r IgG1-peptide-correlations, results='asis'}

if (length(params$peptide_correlation_plots) > 0) {
  for (plot in params$peptide_correlation_plots) {
    p <- plotly::ggplotly(plot, tooltip = "text")
    print(htmltools::tagList(p))
  }
}
```

IgG1 quantitation plot:

```{r IgG1-quantitation-plot, results='asis'}

if (!is.null(params$quantitation_plot)) {
  p <- plotly::ggplotly(params$quantitation_plot, tooltip = "text") %>% 
    GlycoDash::hide_outliers(.)
  print(htmltools::tagList(p))
}
```

## Glycosylation traits

```{r derived-traits-formulas, results='asis'}

if (!is.null(params$formulas)) {
  cat("Glycosylation traits were calculated automatically as follows:")
  params$formulas %>% 
    kableExtra::kbl() %>%
    kableExtra::kable_styling(bootstrap_options = "striped",
                              full_width = F,
                              position = "left") %>%
    htmltools::HTML() %>%
    print()
}

```

```{r custom-traits-formulas, results='asis'}

if (!is.null(params$custom_formulas)) {
  cat("Custom glycosylation traits were calculated as follows:")
  params$custom_formulas %>% 
    dplyr::rename(Cluster = cluster, Trait = custom_trait, Formula = formula) %>% 
    kableExtra::kbl() %>%
    kableExtra::kable_styling(bootstrap_options = "striped",
                              full_width = F,
                              position = "left") %>%
    htmltools::HTML() %>%
    print()
}
```

```{r traits-intensity-plots, results='asis'}

if (!is.null(params$intensity_plots)) {
  purrr::iwalk(params$intensity_plots, function(plot, name) {
    cat("###", name, "\n")
    p <- plotly::ggplotly(plot, tooltip = "text")
    print(htmltools::tagList(p))
  })
}

```

## Repeatability

```{r repeatability, results='asis', warning=FALSE}

purrr::walk(params$repeatability, 
            function(objects_list) {
              if (!is.null(objects_list$plot)) {
                cat("### ",
                    objects_list$title,
                    "\n")
                
                p <- objects_list$plot %>% 
                  plotly::ggplotly(., tooltip = "text")
                
                p <- GlycoDash::change_axis_title_distance(p,
                                                y_distance = 90)
                
                print(htmltools::tagList(p))
              }
              
              if (any(purrr::map(objects_list$plots,
                                 ~ !is.null(.x)))) {
                cat("### ",
                    objects_list$title,
                    "\n")
                
                purrr::walk(objects_list$plots,
                            function(my_plot) {
                              if (!is.null(my_plot)) {
                                p <- my_plot %>% 
                                plotly::ggplotly(., tooltip = "text")
                              
                              p <- GlycoDash::change_axis_title_distance(p,
                                                              y_distance = 90)
                              
                              print(htmltools::tagList(p))
                              }
                            })
              }
              
              if (!is.null(objects_list$table)) {
                objects_list$table %>%
                  dplyr::select(plate, intra_plate_variation) %>% 
                  dplyr::mutate(
                    Plate = plate,
                    `Intra-plate variation (%)` = tidyr::replace_na(
                      as.character(intra_plate_variation), "This plate contained only one sample."),
                    .keep = "unused") %>% 
                  kableExtra::kbl() %>%
                  kableExtra::kable_styling(bootstrap_options = "striped",
                                            full_width = F,
                                            position = "left") %>%
                  htmltools::HTML() %>%
                  print()
                
                cat("\nInter-plate variation: ",
                    signif(mean(objects_list$table$intra_plate_variation, 
                                na.rm = TRUE),
                           digits = 3),
                    " %\n\n")
              }
            })

```

## Data exploration

```{r data-exploration, results='asis', message=FALSE}

reordered_data_exploration <- params$data_exploration[order(names(params$data_exploration))]

purrr::iwalk(reordered_data_exploration, 
             function(objects_list,
                      name) {
               if (!is.null(objects_list$plot)) {
                 cat("### Figure ",
                     gsub(".*([[:digit:]])",
                          "\\1",
                          name),
                     "\n")
                 
                 ggplot_object <- objects_list$plot
                 
                 geoms_in_plot <- sapply(ggplot_object$layers, 
                                         function(x) class(x$geom)[1])
                 
                 plotly_object <- ggplot_object %>% 
                   plotly::ggplotly(., tooltip = "text")
                 
                 if ("GeomBoxplot" %in% geoms_in_plot) {
                   # Determine the number of facets n, the first n traces will correspond to
                   # the boxplot traces in the ggplotly object:
                   boxplot_traces <- 1:GlycoDash::nfacets(ggplot_object)
                   
                   plotly_object <- plotly_object %>% # Use "text" as hoverinfo for the points,
                     # but use the default hoverinfo for the boxplot traces:
                     plotly::style(hoverinfo = "y", traces = boxplot_traces) %>% 
                     # Hide the outliers (needed because plotly ignores "outlier.shape = NA"):
                     GlycoDash::hide_outliers(.) 
                 }
                 
                 print(htmltools::tagList(plotly_object))
                 
               }
             })

```
