---
title: "Data processing report"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
params: 
  lacytools_summary: NA
  plate_design: NA
  sample_list: NA
  metadata: NA
  sample_types_method: NA
  filename_sample_types: NA
  mass_acc: NA
  ipq: NA
  sn: NA
  included_qc: NA
  spectra_curation_tab_contents: NA
  curated_spectra_plot: NA
  curated_spectra_plots: NA
  analyte_curation_method: NA
  ignore_samples: NA
  cut_off_percentage: NA
  analyte_list: NA
  analyte_curation_tab_contents: NA
  derived_traits: NA
  formulas: NA
  repeatability: NA
  data_exploration: NA
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(magrittr)
```

```{r, include=FALSE}
# Init Step to make sure that the dependencies are loaded
htmltools::tagList(DT::datatable(cars))
htmltools::tagList(plotly::ggplotly(ggplot2::ggplot()))
```

## Data import

- LacyTools summary file: `r paste0("\"", params$lacytools_summary, "\"")`
- Plate design file(s): `r paste0("\"", params$plate_design, "\"")`
- Sample list file: `r ifelse(is.null(params$metadata), "none", paste0("\"", params$sample_list, "\""))`
- Metadata file(s): `r ifelse(is.null(params$metadata), "none", paste0("\"", params$metadata, "\""))`

Sample types were added `r ifelse(params$sample_types_method == "Automatically determine sample types based on sample ID's", "automatically", "manually")`.

```{r results='asis'}

if (params$sample_types_method != "Automatically determine sample types based on sample ID's") {
  cat(paste0("Sample types file: \"",
             params$filename_sample_types,
             "\""))
}

```

## Spectra curation

- Analyte quality criteria:
  - Acceptable mass accuracy range: `r min(params$mass_acc)` - `r max(params$mass_acc)`
  - Max. IPQ value: `r params$ipq`
  - Min. S/N ratio: `r params$sn`
  
The following analyte quality criteria were taken into account in the calculation 
of the cut-off for the percentage of passing analytes: `r params$included_qc`

### Spectra curation cut-offs

```{r spectra-curation-cut-offs, results='asis'}

purrr::iwalk(params$spectra_curation_tab_contents, 
             function(objects_list,
                      name) {
               
               cat("####",
                     name,
                     "\n")
               
               objects_list$table %>%
                 kableExtra::kbl() %>%
                 kableExtra::kable_styling(bootstrap_options = "striped",
                                           full_width = F,
                                           position = "left") %>%
                 htmltools::HTML() %>%
                 print()
               
               p <- objects_list$plot %>% 
                 plotly::ggplotly(., tooltip = "text")
               
               p[["x"]][["layout"]][["annotations"]][[2]][["xshift"]] <- -70
               
               p[["x"]][["layout"]][["margin"]][["l"]] <- 90
               
               p <- glycodash::facet_strip_bigger(p)
               
               print(htmltools::tagList(p))
             })

```

### Spectra curation results

```{r spectra-curation-results, results='asis'}

#TODO: add titles

if (!is.null(params$curated_spectra_plot)) {
  p <- params$curated_spectra_plot %>% 
    plotly::ggplotly(., tooltip = "text")
  
  p <- glycodash::facet_strip_bigger(p)
  
  p[["x"]][["layout"]][["annotations"]][[2]][["xshift"]] <- -50
  
  p[["x"]][["layout"]][["annotations"]][[1]][["yshift"]] <- -50
  
  print(htmltools::tagList(p))
} else {
  purrr::iwalk(params$curated_spectra_plots,
             function(curated_spectra_plot,
                      name) {
               
               cat("####",
                     name,
                     "\n")
               
               p <- curated_spectra_plot %>% 
                 plotly::ggplotly(., tooltip = "text")
               
               p <- glycodash::facet_strip_bigger(p)
               
               p[["x"]][["layout"]][["annotations"]][[2]][["xshift"]] <- -50
               
               p[["x"]][["layout"]][["annotations"]][[1]][["yshift"]] <- -50
               
               print(htmltools::tagList(p))
             })
}


```

## Analyte curation

```{r analyte-curation, results='asis'}

if (params$analyte_curation_method == "Curate analytes based on data") {
  text <- paste0(params$ignore_samples, collapse = ", ")
  cat(
      "- Method: based on data\n",
      "- Samples excluded from analyte curation:",
      text,
      "\n- Cut-off percentage:",
      params$cut_off,
      "%")
}

if (params$analyte_curation_method == "Supply an analyte list") {
  cat(
    "- Method: based on analyte list\n",
    "- Analyte list file: \"",
    params$analyte_list,
    "\""
  )
}

```


```{r analyte-curation-plot-table, results='asis'}

if (params$analyte_curation_method == "Curate analytes based on data") {
  
  purrr::iwalk(params$analyte_curation_tab_contents, 
               function(objects_list,
                        name) {
                 cat("###",
                     name,
                     "\n")
                 
                 p <- objects_list$plot %>% 
                   plotly::ggplotly(., tooltip = "text")
                 
                 p[["x"]][["layout"]][["annotations"]][[2]][["xshift"]] <- -50
                 
                 p[["x"]][["layout"]][["annotations"]][[1]][["yshift"]] <- -90
                 
                 print(htmltools::tagList(p))
                 
                 objects_list$analytes_to_include %>% 
                   tidyr::pivot_wider(names_from = "charge",
                                      names_glue = "{charge} charge state included?",
                                      values_from = "charge",
                                      values_fn = function(value) { "Yes" },
                                      values_fill = "No") %>%
                   kableExtra::kbl() %>%
                   kableExtra::kable_styling(bootstrap_options = "striped",
                                             full_width = F,
                                             position = "left") %>%
                   kableExtra::scroll_box(height = "500px", width = "100%") %>% 
                   htmltools::HTML() %>%
                   print()
                 
               })
               
               }

```

## Derived traits

```{r derived-traits, results='asis'}

if (is.null(params$derived_traits)) {
  cat("No derived traits were calculated")
} else {
  cat("The following derived traits were calculated:\n\n- ",
      paste(params$derived_traits, collapse = "\n- "))
}

```

Formulas used to calculate the derived traits:

```{r derived-traits-formulas, results='asis'}

if (!is.null(params$formulas)) {
  params$formulas %>% 
    kableExtra::kbl() %>%
    kableExtra::kable_styling(bootstrap_options = "striped",
                              full_width = F,
                              position = "left") %>%
    htmltools::HTML() %>%
    print()
}

```


## Repeatability

```{r repeatability, results='asis', warning=FALSE}

purrr::walk(params$repeatability, 
            function(objects_list) {
              if (!is.null(objects_list$plot)) {
                cat("### ",
                    objects_list$title,
                    "\n")
                
                p <- objects_list$plot %>% 
                  plotly::ggplotly(., tooltip = "text")
                
                p <- glycodash::change_axis_title_distance(p,
                                                y_distance = 90)
                
                print(htmltools::tagList(p))
              }
              
              if (any(purrr::map(objects_list$plots,
                                 ~ !is.null(.x)))) {
                cat("### ",
                    objects_list$title,
                    "\n")
                
                purrr::walk(objects_list$plots,
                            function(my_plot) {
                              if (!is.null(my_plot)) {
                                p <- my_plot %>% 
                                plotly::ggplotly(., tooltip = "text")
                              
                              p <- glycodash::change_axis_title_distance(p,
                                                              y_distance = 90)
                              
                              print(htmltools::tagList(p))
                              }
                            })
              }
              
              if (!is.null(objects_list$table)) {
                objects_list$table %>%
                  dplyr::select(plate, intra_plate_variation) %>% 
                  dplyr::mutate(
                    Plate = plate,
                    `Intra-plate variation (%)` = tidyr::replace_na(
                      as.character(intra_plate_variation), "This plate contained only one sample."),
                    .keep = "unused") %>% 
                  kableExtra::kbl() %>%
                  kableExtra::kable_styling(bootstrap_options = "striped",
                                            full_width = F,
                                            position = "left") %>%
                  htmltools::HTML() %>%
                  print()
                
                cat("\nInter-plate variation: ",
                    signif(mean(objects_list$table$intra_plate_variation, 
                                na.rm = TRUE),
                           digits = 3),
                    " %\n\n")
              }
            })

```

## Data exploration

```{r data-exploration, results='asis', message=FALSE}

reordered_data_exploration <- params$data_exploration[order(names(params$data_exploration))]

purrr::iwalk(reordered_data_exploration, 
             function(objects_list,
                      name) {
               if (!is.null(objects_list$plot)) {
                 cat("### Figure ",
                     gsub(".*([[:digit:]])",
                          "\\1",
                          name),
                     "\n")
                 
                 ggplot_object <- objects_list$plot
                 
                 geoms_in_plot <- sapply(ggplot_object$layers, 
                                         function(x) class(x$geom)[1])
                 
                 plotly_object <- ggplot_object %>% 
                   plotly::ggplotly(., tooltip = "text")
                 
                 if ("GeomBoxplot" %in% geoms_in_plot) {
                   # Determine the number of facets n, the first n traces will correspond to
                   # the boxplot traces in the ggplotly object:
                   boxplot_traces <- 1:nfacets(ggplot_object)
                   
                   plotly_object <- plotly_object %>% # Use "text" as hoverinfo for the points,
                     # but use the default hoverinfo for the boxplot traces:
                     plotly::style(hoverinfo = "y", traces = boxplot_traces) %>% 
                     # Hide the outliers (needed because plotly ignores "outlier.shape = NA"):
                     hide_outliers(.) 
                 }
                 
                 print(htmltools::tagList(plotly_object))
                 
               }
             })

```

