---
title: "Report"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
params: 
  summary_filenames: NA
  plate_design: NA
  metadata: NA
  sample_types_method: NA
  filename_sample_types: NA
  mass_acc: NA
  ipq: NA
  sn: NA
  spectra_curation_cut_off: NA
  spectra_curation_plot: NA
  analyte_curation_method: NA
  ignore_samples: NA
  cut_off_percentage: NA
  analyte_list: NA
  analyte_curation_objects: NA
  derived_traits: NA
  custom_traits_colnames: NA
  repeatability_1: NA
  repeatability_2: NA
  data_exploration_plot: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(magrittr)
```

## Data import

-   LaCyTools summary files: `r paste0("\"", params$summary_filenames, "\"")`
-   Plate design file(s): `r paste0("\"", params$plate_design, "\"")`
-   Metadata file(s): `r ifelse(is.null(params$metadata), "none", paste0("\"", params$metadata, "\""))`

Sample types were added `r ifelse(params$sample_types_method == "Automatically determine sample types based on sample ID's", "automatically", "manually")`.

```{r results='asis'}

if (params$sample_types_method == "Automatically determine sample types based on sample ID's") {
  cat(paste0("Sample types file: \"",
             params$filename_sample_types,
             "\""))
}

```

## Spectra curation

-   Analyte quality criteria:
    -   Acceptable mass accuracy range: `r min(params$mass_acc)` - `r max(params$mass_acc)`
    -   Max. IPQ value: `r params$ipq`
    -   Min. S/N ratio: `r params$sn`
-   Basis for spectra curation cut-off: `r params$spectra_curation_cut_off`

Show if manual cut-offs were used instead, show separately for specific and total if contains_total_and_specific_samples is TRUE For each cluster: show the plot and table with cut-offs

```{r spectra-curation-plot, results='markup'}

params$spectra_curation_plot +
  ggplot2::theme(text = ggplot2::element_text(size = 12))

```

## Analyte curation

```{r analyte-curation, results='asis'}

if (params$analyte_curation_method == "Curate analytes based on data") {
  text <- paste0(params$ignore_samples, collapse = ", ")
  cat(
      "- Method: based on data\n",
      "- Samples excluded from analyte curation:",
      text,
      "\n- Cut-off percentage:",
      params$cut_off,
      "%")
}

if (params$analyte_curation_method == "Supply an analyte list") {
  cat(
    "- Method: based on analyte list\n",
    "- Analyte list file: \"",
    params$analyte_list,
    "\""
  )
}

```

```{r analyte-curation-plot-table, results='asis'}

if (params$analyte_curation_method == "Curate analytes based on data") {
  
  silent_map <- purrr::imap(params$analyte_curation_objects, 
                            function(objects_list,
                                     name) {
                              cat("###",
                                  name,
                                  "\n")
                              
                              objects_list$table %>% 
                                kableExtra::kbl() %>% 
                                kableExtra::kable_styling(bootstrap_options = "striped", 
                                                          full_width = F, 
                                                          position = "left") %>% 
                                htmltools::HTML() %>% 
                                print()
                              
                              print(objects_list$plot)
                            })
}

```

## Glycosylation traits

```{r derived-traits, results='asis'}

#TODO Try to list the custom traits here as well, using "custom_traits_colnames"

if (is.null(params$derived_traits)) {
  cat("No glycosylation traits were calculated automatically")
} else {
  cat("The following glycosylation traits were calculated automatically:\n\n- ",
      paste(params$derived_traits, collapse = "\n- "))
}

```

## Repeatability

```{r repeatability-first-tab, results='asis', warning=FALSE}

if (!is.null(params$repeatability_1)) {
  cat("###",
      params$repeatability_1$title_for_report,
      "\n")
  
  params$repeatability_1$for_table %>% 
    kableExtra::kbl() %>% 
    kableExtra::kable_styling(bootstrap_options = "striped", 
                              full_width = F, 
                              position = "left") %>% 
    htmltools::HTML() %>% 
    print()
  
  print(params$repeatability_1$plot)
}

```

```{r repeatability-second-tab, results='asis', warning=FALSE}

if (!is.null(params$repeatability_2)) {
  cat("###",
      params$repeatability_2$title_for_report,
      "\n")
  
  params$repeatability_2$for_table %>% 
    kableExtra::kbl() %>% 
    kableExtra::kable_styling(bootstrap_options = "striped", 
                              full_width = F, 
                              position = "left") %>% 
    htmltools::HTML() %>% 
    print()
  
  print(params$repeatability_2$plot)
}

```

## Data exploration

```{r data-exploration-plot, results='markup'}

if (!is.null(params$data_exploration_plot)) {
  print(params$data_exploration_plot)
}

```
