---
title: "Report"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
params: 
  lacytools_summary: NA
  plate_design: NA
  metadata: NA
  sample_types_method: NA
  filename_sample_types: NA
  mass_acc: NA
  ipq: NA
  sn: NA
  spectra_curation_tab_contents: NA
  curated_spectra_plot: NA
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(magrittr)
```


```{r, include=FALSE}
# Init Step to make sure that the dependencies are loaded
htmltools::tagList(DT::datatable(cars))
htmltools::tagList(plotly::ggplotly(ggplot2::ggplot()))
```

## Data import

- LacyTools summary file: `r paste0("\"", params$lacytools_summary, "\"")`
- Plate design file(s): `r paste0("\"", params$plate_design, "\"")`
- Metadata file(s): `r ifelse(is.null(params$metadata), "none", paste0("\"", params$metadata, "\""))`

Sample types were added `r ifelse(params$sample_types_method == "Automatically determine sample types based on sample ID's", "automatically", "manually")`.

```{r results='asis'}

if (params$sample_types_method != "Automatically determine sample types based on sample ID's") {
  cat(paste0("Sample types file: \"",
             params$filename_sample_types,
             "\""))
}

```

## Spectra curation

- Analyte quality criteria:
  - Acceptable mass accuracy range: `r min(params$mass_acc)` - `r max(params$mass_acc)`
  - Max. IPQ value: `r params$ipq`
  - Min. S/N ratio: `r params$sn`

### Cut-offs

```{r spectra-curation-cut-offs, results='asis'}

purrr::iwalk(params$spectra_curation_tab_contents, 
             function(objects_list,
                      name) {
               cat("####",
                   name,
                   "\n")
               
               objects_list$table %>%
                 kableExtra::kbl() %>%
                 kableExtra::kable_styling(bootstrap_options = "striped",
                                           full_width = F,
                                           position = "left") %>%
                 htmltools::HTML() %>%
                 print()
               
               p <- objects_list$plot %>% 
                 plotly::ggplotly(., tooltip = "text")
               
               p[["x"]][["layout"]][["annotations"]][[2]][["xshift"]] <- -70
               
               p[["x"]][["layout"]][["margin"]][["l"]] <- 90
               
               p <- facet_strip_bigger(p)
               
               print(htmltools::tagList(p))
             })

```

### Results

```{r spectra-curation-results, results='asis'}

p <- params$curated_spectra_plot %>% 
  plotly::ggplotly(., tooltip = "text")

p <- facet_strip_bigger(p)

p[["x"]][["layout"]][["annotations"]][[2]][["xshift"]] <- -50

p[["x"]][["layout"]][["annotations"]][[1]][["yshift"]] <- -50

print(htmltools::tagList(p))

```

